Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-12 paper/main.tex
[issue 0.3] shorten section 6.1

With machine learning, we can use algorithms to automatically create
accurate source catalogs with well-calibrated posterior probabilities.
Machine learning techniques have been a popular tool
in many areas of astronomy~\citep{ball2008robust,
banerji2010galaxy,
carrascokind2013tpz,
ivezic2014statistics,
kamdar2016machine1}. 
Artificial neural networks were first applied to the problem of star-galaxy
classification in the work of \citet{odewahn1992automated},
and they have become a core part of the astronomical image processing software
\texttt{SExtractor}~\citep{bertin1996sextractor}.
Other successfully implemented examples of applying machine learning to
the star-galaxy classification problem include decision 
trees~\citep{weir1995automated,suchkov2005census,ball2006robust,sevilla2015effect}, 
Support Vector Machines~\citep{Fadely2012}, and
classifier combination strategies~\citep{kim2015hybrid}.

@@

Probabilistic classification models can be considered as
functions that output a probability estimate of each source
to be in one of the classes (\eg a star or a galaxy).
The simplest way to use the probability output is to
convert it into a class label by using a threshold (a probability cut).
Although many studies often choose the threshold by setting it to a fixed value,
such as $P_{\rmn{cut}} = 0.5$ \citep[\eg][]{henrion2011bayesian, Fadely2012},
choosing $0.5$ as a threshold is not the best choice
for an unbalanced data set, where galaxies outnumber stars.
Furthermore, setting a fixed threshold ignores the operating condition 
(\eg science requirements, stellar distribution, misclassification costs)
where the model will be applied.

@@

When we have no information about the operating condition
when evaluating the performance of classifiers,
there are effective tools such as
the Receiver Operating Characteristic (ROC) curve
\citep*{swets2000better}.
An ROC curve is a graphical plot that illustrates the true positive rate
versus the false positive rate of a binary classifier
as its classification threshold is varied.
The Area Under the Curve (AUC) summarizes the curve information
in a single number,
and can be used as an assessment of the overall performance.

@@

In astronomical applications,
the operating condition usually translates to
the completeness and purity requirements of the star or galaxy sample.
We define the galaxy \textit{completeness}
$c_g$ (also known as recall or sensitivity) as
the fraction of the number of true galaxies classified as galaxies
out of the total number of true galaxies,
\begin{equation}
c_g = \frac{N_g}{N_g + M_g},
\end{equation}

\noindent
where $N_g$ is the number of true galaxies classified as galaxies,
and $M_g$ is the number of true galaxies classified as stars.
We define the galaxy \textit{purity} $p_g$ (also known as precision
or positive predictive value)
as the fraction of the number of true galaxies classified as galaxies
out of the total number of objects classified as galaxies, 
\begin{equation}
p_g = \frac{N_g}{N_g + M_s},
\end{equation}

\noindent
where $M_s$ is the number of true stars classified as galaxies.
Star completeness and purity are defined in a similar manner.

One of the advantages of a probabilistic classification is
that the threshold can be adjusted to produce
a more complete but less pure sample,
or a less complete but more pure one.
We can compare the performance of different classification techniques
by assuming an arbitrary operating condition.
For example, weak lensing science measurements
of the DES require $c_g > 0.960$ and $p_g > 0.778$
to control both the statistical and systematic errors
on the cosmological parameters,
and $c_s > 0.250$ and $p_s > 0.970$
for stellar Point Spread Function (PSF) calibration
\citep{soumagnac2013star}.
Although these values will likely be different
for the science cases of the CFHTLenS data,
we adopt these values to compare the classification performance
at a reasonable operating condition.
Thus, we compute $p_{g}$ at $c_g=0.960$
and $c_{s}$ at $p_s=0.970$.

>>>>

With machine learning, we can use algorithms to automatically create
accurate source catalogs with well-calibrated posterior probabilities.
Machine learning techniques have been a popular tool
in many areas of astronomy~\citep{ball2008robust,
banerji2010galaxy,
carrascokind2013tpz,
ivezic2014statistics,
kamdar2016machine1}. 
Artificial neural networks were first applied to the problem of star-galaxy
classification in the work of \citet{odewahn1992automated},
and they have become a core part of the astronomical image processing software
\texttt{SExtractor}~\citep{bertin1996sextractor}.
Other successfully implemented examples of applying machine learning to
the star-galaxy classification problem include decision 
trees~\citep{weir1995automated,suchkov2005census,ball2006robust,sevilla2015effect}, 
Support Vector Machines~\citep{Fadely2012}, and
classifier combination strategies~\citep*{kim2015hybrid}.

@@

\changed{
Probabilistic classifiers, rather than only assigning discrete labels to each
source, produce a continuous probability distribution of whether each source is
a star or a galaxy.
To evaluate the performance of probabilistic classifiers,
many studies~\citep[\eg][]{henrion2011bayesian, Fadely2012} convert
probability estimates into class labels by choosing a probability
threshold, \eg a source is classified as a star if $P_{\rmn{class}} < 0.5$,
and a galaxy if $P_{\rmn{class}} > 0.5$.
However, using a fixed threshold ignores the model's operating conditions,
such as science requirements, misclassification costs, and stellar distribution.
Furthermore, the probability threshold of 0.5 is not necessarily optimal for
an unbalanced data set, where galaxies outnumber stars.
Following \citet{kim2015hybrid}, we use performance metrics that are well-suited
for probabilistic classifiers: Area Under the Curve (AUC)
for the Receiver Operating Characteristic (ROC) curve, completeness and purity,
and the Mean Squared Error (MSE).
To evaluate 
we also use the calibration error and the absolute error in the estimation
of number of galaxies as performance metrics.
}

@@

\changed{
A Receiver Operating Characteristic (ROC) curve is the
most commonly used method for evaluating the overall performance of a binary
classifier~\citep*{swets2000better}.
In an ROC curve, we plot the true positive rate as a function of the false
positive rate by varying the classification threshold.
The Area Under the Curve (AUC) quantifies the overall performance in a single
number.
}

@@
